### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 1:
    No Comments!

% Reviewer 3:

> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

  Pt #1:
-------- Handle by Mukund and Ashutosh --------------
  One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model and that 
  "If the data […] does not have a certain degree of connectivity, 
  this implies that some biological data has been missed" does not 
  justify connectedness as a fundamental and required biological 
  property that all valid models should respect. The intuition of 
  connectedness as a robustness property provided elsewhere in the 
  manuscript helps but it is still not clear what evidence supports 
  the fact that VTSs are indeed robust. In addition, the problem as 
  formulated does not seem to seek the most robust networks as 
  explained in the following.

  Pt #2: 
-------- Handle by Ankit --------------
  I also found the formulation of the main problems with respect 
  to connectedness somewhat confusing. For example, in Sec. 5.1.1 
  and Sec. 5.1.2 the problems are formulated as a search for VTS G 
  such that G is not k-connected. Yet, Sec. 5.1 specifies that 
  "In case the formula is satisfiable the procedure terminates and 
   we report the value of k", which seems contradictory. Finally, 
   it is not clear why the goal is to find the minimum graph 
   connectivity, given that larger connectivity corresponds to a 
   more robust network. I was expecting an approach involving 
   incrementing k to find the smallest value that makes the formula 
   unsatisfiable, thus identifying the maximum graph connectedness 
   possible for a given VTS with all other constraints being 
   satisfied. However, to the best of my understanding, this is not 
   what the paper is currently proposing, or else further  
   clarifications are needed.

  Pt #3: 
-------- Handle by Ashutosh --------------   
  Another point that should be revised further is around 
  clarifying the contributions of this paper. The response 
  document summarizes nicely that, together with additional 
  QBF encoding, "this paper brings together all the results 
  with extended experiments and more detailed expositions for 
  the benefit of both biological and computation community." 
  However, I did not find a similar concise statement of the 
  contributions in the text. In addition, some of the stated 
  advances over previous approaches seem incremental and minor. 
  For example, for the previous CBMC-based method it is stated 
  that "...the scalability of the method was insufficient. 
  The tool was able to handle the system with just eight 
  compartments". Yet, we learn that "A typical eukaryotic 
  cell contains 9 organelles" and even one of the methods 
  presented in this paper fails for some of the experimental 
  evaluations with 7 or more compartments. The contributions 
  of this work, perhaps in the integration and evaluation of
  several methods reported previously, should be stated clearly 
  and accurately in the main text.

  Pt #4: 
-------- Handle by Ankit and Ashutosh--------------  
  A final minor point is about the use of "Synthesis" as 
  an encoding in Fig 4 and the relevant explanations. 
  Since the other problems list verification techniques 
  and solvers (e.g. BMC, SMT, QBF) and no novel synthesis 
  algorithms were developed for this problem, it would be 
  more appropriate to specify QBF as the encoding used for 
  the "VTS synthesis" problem.

% Reviewer 4:

  Pt #1:
-------- Handle by Somya--------------  
  Point 6 on page 3 is the same as point 4.

  Pt #2:
-------- Handle by Somya--------------  
  I would argue still that the biological section has 
  unnecessary detail and could be simplified further.

  Pt #3:
-------- Handle by Somya--------------  
  That the steady-state condition corresponds to the 
  biological meaning of homeostasis is repeated. This 
  only needs to be mentioned once.

  Pt #4:
-------- Handle by Ankit--------------  
   There is overlap in the 3rd and 6th paragraphs of 
   the 'Related Work' section, which refer to the use 
   of SAT/SMT in GRNs.

Minor points: 
-------- Handle by Lakhsman--------------   
  Small typos / grammatical errors. There are a number 
  of these throughout the text, some of which are listed 
  below (this is not exhaustive, so I recommend carefully 
  reading the manuscript to ensure clarity):

  Page 2, lines 11-12: Understanding how membrane traffic 
  functions *is*, therefore,…

  Page 2, line 13: Cell biologists have made… (not 'The')

   Page 3, line 14: "…parts of the traffic system that 
   *are* unchanging…"

   Page 4, line 6: "We also worked on the synthesis of the 
   unknown pieces *that* may be assisted…" Just after this: 
   "In the work, we developed *an* encoding for the 
    synthesis problem."

   Figure 1 legend, line 44: "typical" not "typic"

   Page 7, line 11: "We have tried to capture important 
   *aspects* of *the* Rothman-Schekman-Sudhof (RSS) model 
   of *the* vesicle…" Also "components" not "component"

   Example 1, line 40: "labels are a set of molecules"

   Example 2, line 36: "Fig. 3b presents its complete output VTS."

   Page 14, line 16: "We will also seek *to answer* two 
   kinds of questions, *given* the property."

   Page 15, line 14: "to ensure the k to be the least one" 
   -> "to ensure that k is minimized"

   Page 22: "The specification for *the* universal condition 
   *described in* Section 5"

### 2019-09-09 papers/journal/bio.tex

	\caption{(A) Schematic of the vesicle transport system. Steps involved in vesicle transport between
		two compartments: a source and a target compartment, are shown. The symbols used for different
		molecules involved in vesicle traffic are explained in the key. At the source compartment,
		transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, different colours
		indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming
		vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple
		types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin
		protein. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and
		the vesicle is recognized and bound by a tethering complex which is linked to the target compartment.
		At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents. (B)
		SNARE regulation network. Here, the dark blue, light blue, green and red stripes represent Qa, Qb,
		Qc and R SNAREs respectively. These 4 SNAREs interact to form a SNARE complex. SNARE
		complex formation is regulated by SM proteins and Sec 17/18. SM proteins inhibit SNARE complex
		formation by inactivating Qa SNAREs. They also enhance SNARE complex formation by stabilizing
		intermediate structures, and by inhibiting premature SNARE complex resolution. Sec17/18 aid in
		SNARE complex resolution. (C) A schematic of the typic eukaryotic cell's VTS. Large circles
		represent compartments, and edges represent vesicle routes. Identities of compartments are written
		inside or beside them; ER = endoplasmic reticulum, Golgi = Golgi apparatus, PM = plasma
		membrane, EE = early endosome, LE = late endosome, Lys = lysosome. The two major vesicle routes;
		the secretory and the endocytic routes are in blue and orange, respectively. The routes in green
		represent vesicles that allow cross-talk between the secretory and the endocytic routes. }
    \label{fig:vts}
\end{figure}

@@

\subsection{The model}
\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
\item Molecules are neither created nor destroyed~\cite{he2009differential}.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
. 
\end{enumerate}
%
All our assumptions, except assumption 5, are held up by cell biological results.
%
Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
%The assumptions 
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
\input{fig3}
\begin{example}
	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} present it's complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes. This synthetic example is a sub-graph of the VTS shown in the \ref{fig:mukund-vts}. Please refer to \ref{sec:ex-vts} for complete detail. 
	%The presented graph is a subgraph of a VTS discussed in details in appendix.
\end{example}

>>>>

	\caption{(A) Schematic of the vesicle transport system. Steps involved in vesicle transport between
		two compartments: a source and a target compartment, are shown. The symbols used for different
		molecules involved in vesicle traffic are explained in the key. At the source compartment,
		transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, different colours
		indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming
		vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple
		types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin
		protein. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and
		the vesicle is recognized and bound by a tethering complex which is linked to the target compartment.
		At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents. (B)
		SNARE regulation network. Here, the dark blue, light blue, green and red stripes represent Qa, Qb,
		Qc and R SNAREs respectively. These 4 SNAREs interact to form a SNARE complex. SNARE
		complex formation is regulated by SM proteins and Sec 17/18. SM proteins inhibit SNARE complex
		formation by inactivating Qa SNAREs. They also enhance SNARE complex formation by stabilizing
		intermediate structures, and by inhibiting premature SNARE complex resolution. Sec17/18 aid in
		SNARE complex resolution. (C) A schematic of the typical eukaryotic cell's VTS. Large circles
		represent compartments, and edges represent vesicle routes. Identities of compartments are written
		inside or beside them; ER = endoplasmic reticulum, Golgi = Golgi apparatus, PM = plasma
		membrane, EE = early endosome, LE = late endosome, Lys = lysosome. The two major vesicle routes;
		the secretory and the endocytic routes are in blue and orange, respectively. The routes in green
		represent vesicles that allow cross-talk between the secretory and the endocytic routes. }
    \label{fig:vts}
\end{figure}

@@

\subsection{The model}
\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspects of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic components and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
\item Molecules are neither created nor destroyed~\cite{he2009differential}.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
. 
\end{enumerate}
%
All our assumptions, except assumption 5, are held up by cell biological results.
%
Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
%The assumptions 
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecules, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
\input{fig3}
\begin{example}
	In Fig.~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Fig.~\ref{fig:synth-vts2} presents its complete output VTS. Every molecule present on the node is active. The activity of the molecules on an edge is determined by the presence of the other molecules. Each label represent particular type of molecule. The synthesis is performed against the stability and 3-connectivity. Synthesized edge is in red color and synthesized molecules are presented in blue. The synthesis adds one edge and 7 molecules to complete the partial VTS. For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes. This synthetic example is a sub-graph of the VTS shown in the \ref{fig:mukund-vts}. Please refer to \ref{sec:ex-vts} for complete detail. 
	%The presented graph is a subgraph of a VTS discussed in details in appendix.
\end{example}
